\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}

\noindent\textbf{Sahil Bansal}\\
Department of Computer Science and Engineering\\
Indian Institute of Technology Kanpur, India\\
\textit{Email: bsahil@iitk.ac.in}\\
\hline
\hline
\vspace{0.1 cm}
\noindent I am a Junior Undergradute student in the Department of Computer Science and Engineering at IIT Kanpur. I am a dedicated, organized and methodical individual. I have good interpersonal skills, am an excellent team worker and am keen and very willing to learn and develop new skills. I have an active and dynamic approach to work and getting things done. I am determined and decisive. I identify and develop opportunities.
\vspace{0.1 cm}
\hline
\hline
\section*{\fontsize{10}{12}\selectfont Education}
\vspace*{-5mm}
\begin{table}[h!]
\begin{tabular}{|c|c|c|c|}
\hline
AISSCE & $2015$ & Aggarsain Public School, Kurukshetra & $10.0$ \\
\hline
AISSE & $2013$ & Aggarsain Public School, Kurukshetra & $95\%$ \\
\hline
B.Tech & $2015-19$ & Indian Institute of Technology, Kanpur & $9.1$ \\
\hline
\end{tabular}
\end{table}
\vspace*{-5mm}
\section*{\fontsize{10}{12}\selectfont Course details}
\vspace*{-5mm}
\begin{table}[h!]
\begin{tabular}{|c|c|c|}
\hline
{\bf Semester} & {\bf Total credits} & {\bf Highlights}\\
\hline
Jan $2016$ - May $2016$ & $50$ & ESC$101$A \\
\hline
Aug $2016$ - Dec $2016$ & $59$ & ESC$201$A \\
\hline
Jan $2017$ - May $2017$ & $64$ & MSO$201$A \\
\hline
Aug $2017$ - Dec $2017$ & $55$ & ESO$207$A \\
\hline
\end{tabular}
\end{table}
\vspace*{-5mm}
\section*{\fontsize{10}{12}\selectfont Skills}
\vspace*{-2mm}
Computer Science\hspace{1.73 cm}:   Operating Systems, Machine Learning\\
Programming Languages\hspace{0.7 cm}:   C, C++, Java, Scripting Languages (bash, awk)\\
\vspace*{-5mm}
\section*{\fontsize{10}{12}\selectfont Projects}
\vspace*{-2mm}
\begin{enumerate}
    \item Adaptive Frequency Estimation Using Iterative DESA with RDFT Based Filter. Combined Discrete Energy Separation Algorithm (DESA-1) and Recursive Discrete Fourier Transform (RDFT)-Based Filter to design a new technique for Grid Voltage Frequency Estimation. Proposed technique is computationally efficient and also robust to negative effects caused by noise and harmonics. Learnt about DFT, FFT, DESA-1, DESA-1a, DESA-2, Teager Energy Operator (TEO) and many other techniques involved in Instantaneous Frequency Estimation.
    \item Biodegradable Systematic Manure Machine. Built a Biodegradable Systematic Manure Machine using Manufacturing Processes such as Drilling, Turning, Milling etc. Aim of Machine is to reduce the biodegradable waste into smallest size possible. Worked in a team of 8 members and a guide.
    \item Beverage Can Vending Machine. Built a Beverage Can Vending Machine using Manufacturing Processes such as Welding, Brazing, Casting, Sheet Metal Working etc. Aim of Machine is to dispense beverages to customers automatically, after the customer inserts currency or credit into the machine. Worked in a team of 4 members, 1st team to attempt this project since years.
\end{enumerate}
\vspace*{-2mm}
\section*{\fontsize{10}{12}\selectfont Awards and Achievements}
\vspace*{-2mm}
\begin{itemize}
    \item[--] Academic Excellence Award, Awarded to top $5\%$ students on the basis of academic performance
    \item[--] All India Rank $571$, Among $1.5$ lakh candidates in JEE ADVANCED
    \item[--] All India Rank $1764$, Among $13$ lakh candidates in JEE MAIN
    \item[--] Appreciation Letter, Signed letter of appreciation by erstwhile HRD Minister for Class-$12$ CBSE Result
    \item[--] Manmohan Singhal Memorial Award, Awarded for being Best All Rounder (Senior Category)
    \item[--] International Rank $65$ \& State Rank $2$, International Mathematics Olympiad
    \item[--] International Rank $221$ \& State Rank $13$, National Science Olympiad
    \item[--] State Rank $4$ \& Zonal Rank $1$, State Level Science Quiz Contest
\end{itemize}
\vspace*{-2mm}
\section*{\fontsize{10}{12}\selectfont Hobbies}
\vspace*{-2mm}
\begin{itemize}
    \item[--] Sports: Cricket, Badminton, Table-Tennis
    \item[--] Music: Guitar, Piano
    \item[--] Others: Watching T.V.
\end{itemize}

\end{document}
